salad

### 2023-11-09 inst/salad.Rmd
consistentification
fixes #155

---
title: "salad"
output: bookdown::html_document2
author: "R. K. S. Hankin"
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a.
This short document shows how to apply `hyper2` idiom to the `salad`
dataset of the `prefmod` package.  From `salad.Rd`:

@@

The null estimate agrees to six places of decimals with that
presented by Turner:

@@

Turner HL, van Etten J, Firth D, Kosmidis I (2020).  "Modelling
Rankings in R: The PlackettLuce Package."  _Computational Statistics_,
35, 1027–1057. doi:10.1007/s00180-020-00959-3,
\url{https://doi.org/10.1007/s00180-020-00959-3}

Yildiz, Ilkay, Jennifer Dy, Deniz Erdogmus, Jayashree Kalpathy-Cramer,
Susan Ostmo, J. Peter Campbell, Michael F. Chiang, and Stratis
Ioannidis. 2020. "Fast and Accurate Ranking Regression."  In
Proceedings of the Twenty Third International Conference on Artificial
Intelligence and Statistics, edited by Silvia Chiappa and Roberto
Calandra, 108:77–88. Proceedings of Machine Learning
Research. \url{http://proceedings.mlr.press/v108/yildiz20a.html}

>>>>

---
title: "salad"
output: bookdown::html_document2
author: "R. K. S. Hankin"
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017.
This short document shows how to apply `hyper2` idiom to the `salad`
dataset of the `prefmod` package [@hatzinger2012].  From `salad.Rd`:

@@

The null estimate agrees to six places of decimals with that
presented by @turner2020_nomarkup:

@@
